Abstract

### 2025-10-02 output/Main_text.Rmd
Add latent space and "agnostic" plot

@@

```{r item-plot-out}
#| cache:          false
#| fig.cap:   Item Plots in an Orthogonal (Left) and Oblique (Right) Test Space
#| fig.topcaption: true
#| fig.height:     3
#| fig.width:      6.65
#| warning:        false
plot_orth_uncorr_contours + plot_oblique_ts

ggsave(file.path(DOC_DIR, "Figure_1.svg"))
```

>>>>

```{r compose-test-space-orthogonal-plot}
```

```{r compose-latent-space-plot}
```

@@

```{r item-plot-out}
#| cache:          false
#| fig.cap:   Item Plots in an Orthogonal (Left) and Oblique (Right) Test Space
#| fig.topcaption: true
#| fig.height:     5
#| fig.width:      6.65
#| warning:        false
(plot_orth_uncorr_contours + plot_orth_corr) /
  (plot_oblique_ts + plot_oblique_ls)

ggsave(file.path(DOC_DIR, "Figure_1.svg"), width = 6.65, height = 5)
```
